Nearest Neighbour Methods for Length of Stay Prediction

### 2014-12-23 papers/paper.tex
Add skeleton of NN paper

\chapter{Artificial Intelligence in Medicine -- Draft Paper} \label{app:paper}

We are currently in the process of drafting a paper of our results to submit to
Artificial Intelligence in Medicine, a top journal for research that uses
artificial intelligence in fields such as medicine, human biology and health
care. Here we have attached our current draft,
which will be soon ready for submission.

\clearpage

\setlength{\multicolsep}{0pt}
\setlength{\topskip}{\fontcharht\font`B }
\setlength{\parskip}{0pt}
%[
\begin{center}
\section*{Improving the Prediction of Length of Hospital Stay for Trauma Patients}
\end{center}
\begin{multicols}{2}
\begin{center}
Tianyu Pu, Irena Koprinska \\
School of Information Technologies \\
University of Sydney, NSW, 2006 \\
\texttt{\{tianyu.pu,irena.koprinska\}@sydney.edu.au}
\end{center}
\vfill
\columnbreak
\begin{center}
Michael Dinh \\
Trauma Services, Royal Prince Alfred Hospital \\
Sydney, NSW, 2042 \\
\texttt{dinh.mm@gmail.com}
\end{center}
\end{multicols}
%]

\begin{multicols}{2}
\subsection*{Abstract}
Predicting the length of hospital stay for injured patients involves making a
judgement about how long they need to be hospitalised, so that doctors and
hospital staff can plan the appropriate course of treatment for the patient
to ensure they recover in the quickest possible time. However, previous studies
have used a limited number of statistical techniques such as logistic
regression in order to predict the length of stay, and have not considered
automatic methods of feature selection.

@@

We were able to achieve improved accuracy and area
under the curve for both data sets, and we also show that our proposed Ranked
Distance Nearest Neighbour improves accuracy and area under the curve over
traditional nearest neighbour algorithms.

\subsection*{Introduction}
Hospitals often have limited funding, and therefore managing and utilising
their resources efficiently has always been a priority \cite{Walczak2003}.
One key measurement of hospital activity, health care utilisation, and hospital
cost is the patient length of stay \citep{Omachonu2004,Ng2006}. The length of
stay has been used in a wide variety of medical domains, such as burns
 \citep{Yang2010}, intensive
care \citep{Tu1993,Harper2005,Perez2006,Dybowski1996},
psychiatry \citep{Lowell1997}, and acute pancreatitis \citep{Pofahl1998}, in
order to assist hospitals in allocating beds and other patient management
resources as efficiently as possible. However, given the many different
conditions that hospitals manage, the length of stay of a patient is
not easy to predict \citep{Walczak2003}, especially upon a patient's admission.
Many methods have been explored in the literature, from the realm of statistics
to techniques in data mining, and they have been explored for many different
medical domains.

@@

\subsection*{Problem Statement}
Our problem is a binary \textit{classification} task in which we
predict one of two possible categories for a patient: a length of stay (LOS) of
less than or equal to 2 days, or a LOS of greater than 2 days.

\subsection*{Ranked Distance Nearest Neighbour}
\paragraph{Intuition}
As we mentioned earlier, all features are considered equally in a $k$-NN
classifier, which implies that all features are equally important in predicting
the class. In practice, however, this is not always the case: to predict the
LOS of a trauma patient, the severity of their injury should affect the final
LOS more than whether or not they can speak English (which could be just two
of many features that are recorded about a patient). Our contribution is a
new NN algorithm that uses a modified distance function which takes into
account the relative importance of all features called Ranked Distance
Nearest Neighbour (RD).

\paragraph{Mathematical formulation}
Given two instances $\mathbf{x} = (x_1,x_2,\ldots,x_n)$ and
$\mathbf{y} = (y_1,y_2,\ldots,y_n)$, the distance between them is given by:
\begin{equation*}
\mathrm{Distance} = \sum_{i=1}^n w_i |x_i-y_i|
\end{equation*}
where the $w_i$s weight the contribution of the $i$-th feature to the overall
distance that is computed by the $k$-NN algorithm. We assume that all feature
values have been normalised, as described above.

\paragraph{Assignment of weights}
The weights $w_i$ can be tuned to match the particular problem that is being
investigated. For our LOS classification problem, we will consider one way
of weighting features.
First, we compute the correlation coefficients as described in the point above.
This gives us a ranking of the importance of each feature to the prediction of
the class, with 1 being the highest rank (indicating the most importance) and
$n$ being the lowest rank (indicating the least importance).
Instead of using the values of the correlation directly to weight
the distance contribution of each feature, we specify a function:
\begin{equation*}
f : \mathrm{Rank} \rightarrow \mathbb{R}, \mathrm{Rank} \in \{1,2,\ldots,n\}
\end{equation*}
that describes
how the weights of the features vary with the rank. This function should
inituitively be non-increasing and should produce lower values when the rank
number is greater, meaning that less important features have a lower weight
in the distance calculation.
Note that choosing $f(\mathrm{Rank}) = k$ for any non-zero constant $k$
results in all features contributing equally to the distance calculation.
We will use $f(\mathrm{Rank}) = \frac{1}{\mathrm{Rank}^c}$, where
$c$ varies from 0 to 1.

\subsection*{Feature Selection}
Here we introduce the feature selection algorithms we evaluate in our work.
Several of these have not been investigated in previous work on length of
stay prediction.
\subsubsection*{Correlation-based Feature Selection}
Correlation-based feature selection (CFS) is a method developed by Hall
\cite{Hall2000} which looks for a subset of features that have high correlation
with the class but low intercorrelation among the features. In this case,
correlation between two features is measured using what is called the
\textit{symmetric uncertainty}:
\begin{equation*}
U(A,B) = 2\dfrac{H(A)+H(B)-H(A,B)}{H(A)+H(B)}
\end{equation*}
where $A$ and $B$ are two nominal attributes and $H$ is the entropy function.
The entropies are calculated from the probabilities of each feature value, and
$H(A,B)$, the joint entropy of $A$ and $B$, is calculated from the
probabilities of each combination of values of $A$ and $B$. Note that $U(A,B)$
is always between 0 and 1.
CFS conducts a search through subsets of all features in order to find the
one feature subset that has the best merit.

\subsubsection*{Pearson Correlation Coefficient}
The Pearson correlation coefficient measures the degree of linear correlation
between two variables. It is always in the range $[-1,1]$, where -1 is total
negative correlation, 0 is no (linear) correlation, and 1 is total positive
correlation. We compute the Pearson correlation between each feature and the
class using:
\begin{equation*}
r_i = \dfrac{\sum_{i=1}^m (x_i-\bar{x})(c-\bar{c})}{\sqrt{(\sum_{i=1}^m x_i-\bar{x})(\sum_{i=1}^m c-\bar{c})}}
\end{equation*}
where $m$ is the number of training examples, $x_i$ is the value of feature
$i$, and $\bar{x}$ and $\bar{c}$ are the arithmetic averages of the feature
values and the class values respectively.

\subsubsection*{Information Gain}
We can also measure the IG of each feature as follows.
If we have a class $C$ and a feature $F$, the entropy of the
class before and after observing the feature is:
\begin{equation*}
\begin{aligned}
& \mathrm{entropy}(C) = - \sum_{c \in C} p(c) \mathrm{log}_2 p(c) \\
& \mathrm{entropy}(C|F) = - \sum_{f \in F} p(f) \sum_{c \in C} p(c|f) \mathrm{log}_2 p(c|f)
\end{aligned}
\end{equation*}
The decrease in entropy reflects the gain in information provided by the
feature and is given by:
\begin{equation*}
IG(C|F) = \mathrm{entropy}(C) - \mathrm{entropy}(C|F)
\end{equation*}

@@

\subsubsection*{1R}
Another way to evaluate the relevance of features is to use the idea behind the
1R classifier described in Section. Recall that the 1R
classifier constructs simple 1-rules based on each feature and uses the feature
that produces the lowest error rate (that is, the highest accuracy) on the data
set to classify unseen examples. These accuracy rates can be calculated for
each feature, which are then used to rank the features from highest to lowest
accuracy.

@@

\subsubsection*{Wrapper-based Feature Selection}
The feature selection methods described above (CFS, Pearson correlation and
1R) have been described as \textit{filter} approaches to attribute selection.
Kohavi and John proposed another approach, the \textit{wrapper} approach:
instead of performing feature selection independently of the learning
algorithm using some measure of ``relevance'',
the learning algorithm itself is used to evaluate the goodness of
subsets of features \cite{Kohavi1997}.

@@

\subsection*{Evaluation Method}
Our evaluation was carried out using a trauma-specific data set
containing 2546 records collected from 2007--2011 collected at a major hospital
in Sydney, Australia.
\subsubsection*{Classifiers}
We tested the performance of Zero-R, 1R, Na\"{i}ve Bayes, C4.5 decision trees,
support vector machines, multi-layer perceptrons, $k$-nearest neighbour with 1
and 20 nearest neighbours, K* and logistic regression, as well as our proposed
Ranked Distance Nearest Neighbour.

\subsubsection*{Procedure}
The steps that we took to evaluate the performance of the various classifiers
and feature selection methods were:
\begin{enumerate}
\item For each data set, we evaluated the effect of the 4 automatic feature
selection methods on each of the 8 classifiers listed above, giving us 32
configurations for each data set, over
4 sets. Evaluation was performed using ten runs of \textit{ten-fold stratified
cross-validation}.
\item For the two trauma LOS data sets, we additionally evaluated the two
manual feature selection methods with all 8 classifiers. Recall from Section
\ref{sec:manual} that one of the feature sets is from the key previous work
on trauma LOS prediction that we use as a baseline, and the other feature set
is a set of features included through consultation with a domain expert.
\end{enumerate}

\subsection*{Results and Discussion}
The best accuracy was 77.81\%, achieved using the $k$-NN algorithm
with 1 nearest neighbour, a discretised data set, and feature selection using a
C4.5 wrapper. The best AUC of 0.846 was achieved using logistic regression with
features selected by a correlation coefficient threshold of 0.1, and again
using the discretised data set.

\begin{figure*}[htbp]
\begin{subfigure}{.48\textwidth}
\includegraphics[width=\textwidth]{images/results/tr-nofs-acc.eps}
\caption{}
\label{}
\end{subfigure}%
\begin{subfigure}{.55\textwidth}
\includegraphics[width=\textwidth]{images/results/tr-nofs-auc.eps}
\caption{}
\label{}
\end{subfigure}

\begin{subfigure}{.48\textwidth}
\includegraphics[width=\textwidth]{images/results/tr-dinh-acc.eps}
\caption{}
\label{}
\end{subfigure}%
\begin{subfigure}{.55\textwidth}
\includegraphics[width=\textwidth]{images/results/tr-dinh-auc.eps}
\caption{}
\label{}
\end{subfigure}

\begin{subfigure}{.48\textwidth}
\includegraphics[width=\textwidth]{images/results/tr-expert-acc.eps}
\caption{}
\label{}
\end{subfigure}%
\begin{subfigure}{.55\textwidth}
\includegraphics[width=\textwidth]{images/results/tr-expert-auc.eps}
\caption{}
\label{}
\end{subfigure}

\begin{subfigure}{.48\textwidth}
\includegraphics[width=\textwidth]{images/results/tr-cfs-acc.eps}
\caption{}
\label{fig:tr-nothreshold-cfs-acc}
\end{subfigure}%
\begin{subfigure}{.55\textwidth}
\includegraphics[width=\textwidth]{images/results/tr-cfs-auc.eps}
\caption{}
\label{}
\end{subfigure}
\caption[]{Comparison of accuracy and AUC between classifiers for each non-threshold feature selection method, grouped by whether or not discretisation was applied.}
\label{fig:tr-nothreshold}
\end{figure*}

@@

\begin{subfigure}{.48\textwidth}
\includegraphics[width=\textwidth]{images/results/tr-wrapper-acc.eps}
\caption{}
\label{}
\end{subfigure}%
\begin{subfigure}{.55\textwidth}
\includegraphics[width=\textwidth]{images/results/tr-wrapper-auc.eps}
\caption{}
\label{}
\end{subfigure}
\caption[]{Comparison of accuracy and AUC between classifiers for each non-threshold feature selection method, grouped by whether or not discretisation was applied.}
\label{}
\end{figure*}

@@

\subsection*{Conclusions}
The best accuracy we achieved on the trauma data was 77.81\% with the $k$-NN
classifier using 1 nearest neighbour and 11 out of 78 features. This represents
an improvement over previous work done by Dinh et al. \cite{Dinh2013a}
on the same data set,
where they managed to achieve 75.06\% with logistic regression. More
importantly, we were able to improve upon their AUC of 0.812 with a result of
0.846, also using logistic regression but first discretising numeric features
and reducing the feature set to 29 features.
If we consider an even smaller number of features, then K*
gives an AUC of 0.838 with 11 features selected by the C4.5 wrapper, which
improves upon the result of Dinh et al. \cite{Dinh2013a} while using a little
more than half
the number of features. The drawback of $k$-NN and K* is that they require all
examples to be stored and then searched during classification, which becomes
storage- and computation-expensive as the data set increases in size.

@@

\end{multicols}

>>>>

\documentclass[10pt]{article}

\usepackage{amsfonts}
\usepackage{amsmath}
\usepackage{amsthm}
\usepackage{graphicx}
\usepackage{multicol}
\usepackage{natbib}
\usepackage{subcaption}

\title{Nearest Neighbour Methods for Length of Stay Prediction}
\author{
  Tianyu Pu, Irena Koprinska, Kalina Yacef\\
  School of Information Technologies\\
  University of Sydney, NSW, 2006\\
  \texttt{\{tianyu.pu,irena.koprinska,kalina.yacef\}@sydney.edu.au}
  \and
  Michael Dinh\\
  Trauma Services, Royal Prince Alfred Hospital\\
  Sydney, NSW, 2042\\
  \texttt{dinh.mm@gmail.com}
}

\date{\today}

\begin{document}
\maketitle

\begin{abstract}
Predicting the length of hospital stay for injured patients involves making a
judgement about how long they need to be hospitalised, so that doctors and
hospital staff can plan the appropriate course of treatment for the patient
to ensure they recover in the quickest possible time. However, previous studies
have used a limited number of statistical techniques such as logistic
regression in order to predict the length of stay, and have not considered
automatic methods of feature selection.

@@

We were able to achieve improved accuracy and area
under the curve for both data sets, and we also show that our proposed Ranked
Distance Nearest Neighbour improves accuracy and area under the curve over
traditional nearest neighbour algorithms.
\end{abstract}

\section{Introduction}
Hospitals often have limited funding, and therefore managing and utilising
their resources efficiently has always been a priority \cite{Walczak2003}.
One key measurement of hospital activity, health care utilisation, and hospital
cost is the patient length of stay \citep{Omachonu2004,Ng2006}. The length of
stay has been used in a wide variety of medical domains, such as burns
 \citep{Yang2010}, intensive
care \citep{Tu1993,Harper2005,Perez2006,Dybowski1996},
psychiatry \citep{Lowell1997}, and acute pancreatitis \citep{Pofahl1998}, in
order to assist hospitals in allocating beds and other patient management
resources as efficiently as possible. However, given the many different
conditions that hospitals manage, the length of stay of a patient is
not easy to predict \citep{Walczak2003}, especially upon a patient's admission.
Many methods have been explored in the literature, from the realm of statistics
to techniques in data mining, and they have been explored for many different
medical domains.

@@

\section{Problem Statement}
Our problem is a binary \textit{classification} task in which we
predict one of two possible categories for a patient: a length of stay (LOS) of
less than or equal to 2 days, or a LOS of greater than 2 days.

\section{Ranked Distance Nearest Neighbour}
\subsection{Intuition}
As we mentioned earlier, all features are considered equally in a $k$-NN
classifier, which implies that all features are equally important in predicting
the class. In practice, however, this is not always the case: to predict the
LOS of a trauma patient, the severity of their injury should affect the final
LOS more than whether or not they can speak English (which could be just two
of many features that are recorded about a patient). Our contribution is a
new NN algorithm that uses a modified distance function which takes into
account the relative importance of all features called Ranked Distance
Nearest Neighbour (RD).

\subsection{Mathematical formulation}
Given two instances $\mathbf{x} = (x_1,x_2,\ldots,x_n)$ and
$\mathbf{y} = (y_1,y_2,\ldots,y_n)$, the distance between them is given by:
\begin{equation*}
\mathrm{Distance} = \sum_{i=1}^n w_i |x_i-y_i|
\end{equation*}
where the $w_i$s weight the contribution of the $i$-th feature to the overall
distance that is computed by the $k$-NN algorithm. We assume that all feature
values have been normalised, as described above.

\subsection{Assignment of weights}
The weights $w_i$ can be tuned to match the particular problem that is being
investigated. For our LOS classification problem, we will consider one way
of weighting features.
First, we compute the correlation coefficients as described in the point above.
This gives us a ranking of the importance of each feature to the prediction of
the class, with 1 being the highest rank (indicating the most importance) and
$n$ being the lowest rank (indicating the least importance).
Instead of using the values of the correlation directly to weight
the distance contribution of each feature, we specify a function:
\begin{equation*}
f : \mathrm{Rank} \rightarrow \mathbb{R}, \mathrm{Rank} \in \{1,2,\ldots,n\}
\end{equation*}
that describes
how the weights of the features vary with the rank. This function should
inituitively be non-increasing and should produce lower values when the rank
number is greater, meaning that less important features have a lower weight
in the distance calculation.
Note that choosing $f(\mathrm{Rank}) = k$ for any non-zero constant $k$
results in all features contributing equally to the distance calculation.
We will use $f(\mathrm{Rank}) = \frac{1}{\mathrm{Rank}^c}$, where
$c$ varies from 0 to 1.

\section{Feature Selection}
Here we introduce the feature selection algorithms we evaluate in our work.
Several of these have not been investigated in previous work on length of
stay prediction.
\subsection{Correlation-based Feature Selection}
Correlation-based feature selection (CFS) is a method developed by Hall
\cite{Hall2000} which looks for a subset of features that have high correlation
with the class but low intercorrelation among the features. In this case,
correlation between two features is measured using what is called the
\textit{symmetric uncertainty}:
\begin{equation*}
U(A,B) = 2\dfrac{H(A)+H(B)-H(A,B)}{H(A)+H(B)}
\end{equation*}
where $A$ and $B$ are two nominal attributes and $H$ is the entropy function.
The entropies are calculated from the probabilities of each feature value, and
$H(A,B)$, the joint entropy of $A$ and $B$, is calculated from the
probabilities of each combination of values of $A$ and $B$. Note that $U(A,B)$
is always between 0 and 1.
CFS conducts a search through subsets of all features in order to find the
one feature subset that has the best merit.

\subsection{Pearson Correlation Coefficient}
The Pearson correlation coefficient measures the degree of linear correlation
between two variables. It is always in the range $[-1,1]$, where -1 is total
negative correlation, 0 is no (linear) correlation, and 1 is total positive
correlation. We compute the Pearson correlation between each feature and the
class using:
\begin{equation*}
r_i = \dfrac{\sum_{i=1}^m (x_i-\bar{x})(c-\bar{c})}{\sqrt{(\sum_{i=1}^m x_i-\bar{x})(\sum_{i=1}^m c-\bar{c})}}
\end{equation*}
where $m$ is the number of training examples, $x_i$ is the value of feature
$i$, and $\bar{x}$ and $\bar{c}$ are the arithmetic averages of the feature
values and the class values respectively.

\subsection{Information Gain}
We can also measure the IG of each feature as follows.
If we have a class $C$ and a feature $F$, the entropy of the
class before and after observing the feature is:
\begin{equation*}
\begin{aligned}
& \mathrm{entropy}(C) = - \sum_{c \in C} p(c) \mathrm{log}_2 p(c) \\
& \mathrm{entropy}(C|F) = - \sum_{f \in F} p(f) \sum_{c \in C} p(c|f) \mathrm{log}_2 p(c|f)
\end{aligned}
\end{equation*}
The decrease in entropy reflects the gain in information provided by the
feature and is given by:
\begin{equation*}
IG(C|F) = \mathrm{entropy}(C) - \mathrm{entropy}(C|F)
\end{equation*}

@@

\subsection{1R}
Another way to evaluate the relevance of features is to use the idea behind the
1R classifier described in Section. Recall that the 1R
classifier constructs simple 1-rules based on each feature and uses the feature
that produces the lowest error rate (that is, the highest accuracy) on the data
set to classify unseen examples. These accuracy rates can be calculated for
each feature, which are then used to rank the features from highest to lowest
accuracy.

@@

\subsection{Wrapper-based Feature Selection}
The feature selection methods described above (CFS, Pearson correlation and
1R) have been described as \textit{filter} approaches to attribute selection.
Kohavi and John proposed another approach, the \textit{wrapper} approach:
instead of performing feature selection independently of the learning
algorithm using some measure of ``relevance'',
the learning algorithm itself is used to evaluate the goodness of
subsets of features \cite{Kohavi1997}.

@@

\section{Evaluation Method}
Our evaluation was carried out using a trauma-specific data set
containing 2546 records collected from 2007--2011 collected at a major hospital
in Sydney, Australia.
\subsection{Classifiers}
We tested the performance of Zero-R, 1R, Na\"{i}ve Bayes, C4.5 decision trees,
support vector machines, multi-layer perceptrons, $k$-nearest neighbour with 1
and 20 nearest neighbours, K* and logistic regression, as well as our proposed
Ranked Distance Nearest Neighbour.

\subsection{Procedure}
The steps that we took to evaluate the performance of the various classifiers
and feature selection methods were:
\begin{enumerate}
\item For each data set, we evaluated the effect of the 4 automatic feature
selection methods on each of the 8 classifiers listed above, giving us 32
configurations for each data set, over
4 sets. Evaluation was performed using ten runs of \textit{ten-fold stratified
cross-validation}.
\item For the two trauma LOS data sets, we additionally evaluated the two
manual feature selection methods with all 8 classifiers. Recall from Section
\ref{sec:manual} that one of the feature sets is from the key previous work
on trauma LOS prediction that we use as a baseline, and the other feature set
is a set of features included through consultation with a domain expert.
\end{enumerate}

\section{Results and Discussion}
The best accuracy was 77.81\%, achieved using the $k$-NN algorithm
with 1 nearest neighbour, a discretised data set, and feature selection using a
C4.5 wrapper. The best AUC of 0.846 was achieved using logistic regression with
features selected by a correlation coefficient threshold of 0.1, and again
using the discretised data set.

\begin{figure*}[htbp]
\begin{subfigure}{.48\textwidth}
\includegraphics[width=\textwidth]{../thesis/images/results/tr-nofs-acc.eps}
\caption{}
\label{}
\end{subfigure}%
\begin{subfigure}{.55\textwidth}
\includegraphics[width=\textwidth]{../thesis/images/results/tr-nofs-auc.eps}
\caption{}
\label{}
\end{subfigure}

\begin{subfigure}{.48\textwidth}
\includegraphics[width=\textwidth]{../thesis/images/results/tr-dinh-acc.eps}
\caption{}
\label{}
\end{subfigure}%
\begin{subfigure}{.55\textwidth}
\includegraphics[width=\textwidth]{../thesis/images/results/tr-dinh-auc.eps}
\caption{}
\label{}
\end{subfigure}

\begin{subfigure}{.48\textwidth}
\includegraphics[width=\textwidth]{../thesis/images/results/tr-expert-acc.eps}
\caption{}
\label{}
\end{subfigure}%
\begin{subfigure}{.55\textwidth}
\includegraphics[width=\textwidth]{../thesis/images/results/tr-expert-auc.eps}
\caption{}
\label{}
\end{subfigure}

\begin{subfigure}{.48\textwidth}
\includegraphics[width=\textwidth]{../thesis/images/results/tr-cfs-acc.eps}
\caption{}
\label{fig:tr-nothreshold-cfs-acc}
\end{subfigure}%
\begin{subfigure}{.55\textwidth}
\includegraphics[width=\textwidth]{../thesis/images/results/tr-cfs-auc.eps}
\caption{}
\label{}
\end{subfigure}
\caption[]{Comparison of accuracy and AUC between classifiers for each non-threshold feature selection method, grouped by whether or not discretisation was applied.}
\label{fig:tr-nothreshold}
\end{figure*}

@@

\begin{subfigure}{.48\textwidth}
\includegraphics[width=\textwidth]{../thesis/images/results/tr-wrapper-acc.eps}
\caption{}
\label{}
\end{subfigure}%
\begin{subfigure}{.55\textwidth}
\includegraphics[width=\textwidth]{../thesis/images/results/tr-wrapper-auc.eps}
\caption{}
\label{}
\end{subfigure}
\caption[]{Comparison of accuracy and AUC between classifiers for each non-threshold feature selection method, grouped by whether or not discretisation was applied.}
\label{}
\end{figure*}

@@

\section{Conclusions}
The best accuracy we achieved on the trauma data was 77.81\% with the $k$-NN
classifier using 1 nearest neighbour and 11 out of 78 features. This represents
an improvement over previous work done by Dinh et al. \cite{Dinh2013a}
on the same data set,
where they managed to achieve 75.06\% with logistic regression. More
importantly, we were able to improve upon their AUC of 0.812 with a result of
0.846, also using logistic regression but first discretising numeric features
and reducing the feature set to 29 features.
If we consider an even smaller number of features, then K*
gives an AUC of 0.838 with 11 features selected by the C4.5 wrapper, which
improves upon the result of Dinh et al. \cite{Dinh2013a} while using a little
more than half
the number of features. The drawback of $k$-NN and K* is that they require all
examples to be stored and then searched during classification, which becomes
storage- and computation-expensive as the data set increases in size.

@@

\bibliographystyle{abbrv}{
  \bibliography{../thesis/references}
}

\end{document}
